Modular Synthesis of Verified Verifiers of Computation with STV Algorithms

### 2019-03-14 paper/paper.tex
my latest changes

This informal description is necessarily imprecise, with details
differing widely between jurisdictions. For example, there are
substantial differences in the details of
precisely which excess ballots are being transferred after
candidates have been elected, or  the order in which surplus ballots are
being transferred.

@@

To exemplify the flexibility of our framework, we discuss an instantiation of the machine with the CADE STV as well. We refer the reader to our source code\footnote{see  \url{https://github.com/MiladKetabGhale/Modular_Checker}} for details of five other STV instances for which we have successfully completed the verifiers synthesis process. 

>>>>

This informal description is necessarily imprecise, with details differing widely between jurisdictions. For example,
the details of precisely which excess ballots are being transferred after candidates have been elected, the order in which surplus ballots are being transferred vary widely between different jurisdictions.

@@

To exemplify the flexibility of our framework, we discuss an instantiation of the machine with the CADE STV as well. We refer the reader to our source code\footnote{see  \url{https://github.com/MiladKetabGhale/Modular_Checker}} for details of four other STV instances for which we have successfully completed the verifiers synthesis process. 
